---
title: "A Forecasting Study on Swedish Wine Sales"
subtitle: "Term Paper Statistical Learning"
author: "Jonathan Berrisch & Timo Rammert"
institute: "Universität Duisburg-Essen"
date: "23.09.2019"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

class: inverse, center, middle

# Introduction

```{r echo=FALSE, include=FALSE}
library(dplyr)
library(plotly)
```

---
class: inverse, center, middle

# Data and Variables

---

# Data and Variables

Data set train:
  - 145179 observations of 58 variables (before preprocessing)
  - 41416 observations of 45 variables (after preprocessing)
  
Data set test:
  - 48395 observations of 58 variables (before preprocessing)
  - xxxxx observations of 45 variables (after preprocessing)
  
Variables: name of wine, country, price, amount sold per week, reviews-related variables, etc.
  
```{r tables-VarType, echo = F}
load("../00_data/output_paper/01_typeof_vec.rda")
knitr::kable(t(typeof_vec), caption = "Frequency of Variable Types.")
```

---
class: inverse, center, middle

# Validation Approach


---


# Analysis

1. Mean Regression and Linear Regression

2. Least Absolute Shrinkage and Selection Operator

3. Principal Components Regression and Partial Least Squares

4. Splines

5. Decision Tree Methods

  5.1. Single Regression Tree

  5.2. Bootstrap Aggregation

  5.3. Random Forest

  5.4. Boosting
  
---
# Analysis

### Mean Regression and Linear Regression

---

<div style="position:absolute;margin-top:0px;Z-index:1">

<h1 id="analysis">Random Forest</h1>

</div>

<div style="position:relative; margin-top:-50px">


```{r, echo=FALSE, message=FALSE}
### Summary Random Forest  ####

# Get filenames
files <- dir(path = "../02_analysis/cv/rf")
df_rf_list <- list()

# Load the data
for(i in 1:(length(files))){
  load(file = paste("../02_analysis/cv/rf/", files[i], sep = ""))
  df_rf_list[[i]] <- cbind(grid, rmse_RF)
  colnames(df_rf_list[[i]]) <- c("mtry", "trees", paste("rmse_fold_",i, sep = ""))
}

# Produce a plot that shows RMSE vs. Hyperparameters
rf_df <- purrr::reduce(df_rf_list, .f = full_join) %>%
  mutate(mean = rowMeans(.[3:7])) %>%
  arrange(desc(mean))

library(plotly)
rf_plot <- plot_ly(x = rf_df$mtry, y = rf_df$trees, z = rf_df$mean,
                   type="scatter3d",
                   mode = "markers",
                   marker = list(color = rf_df$mean,
                                 colorbar = list(title = "RMSE"),
                                 colorscale = list(c(0, 1), c('25c900', 'bf0000')),
                                 showscale = TRUE,
                                 line = list(width = 0), size = 6)) %>% layout(
                                   title = "",
                                   scene = list(
                                     xaxis = list(title = "Vars per Split"),
                                     yaxis = list(title = "Trees"),
                                     zaxis = list(title = "RMSE",
                                                  range=c(4200,10000),
                                                  tick0 = 4500,
                                                  dtick = 1000),
                                     annotations = list(list(
                                       showarrow = T,
                                       z = min(rf_df$mean),
                                       y = rf_df$trees[which.min(rf_df$mean)],
                                       x = rf_df$mtry[which.min(rf_df$mean)],
                                       ay = -150,
                                       ax = 150,
                                       text = "Minimum",
                                       arrowcolor = "black",
                                       arrowsize = 1,
                                       arrowwidth = 1,
                                       arrowhead = 1,
                                       font = list(
                                         size = 14
                                       ))
                                     ))) %>% config(displayModeBar = F)

f <- paste0("p.",i,".html")
htmlwidgets::saveWidget(rf_plot, f)
htmltools::tags$iframe(
    src=f,
    width="100%", 
    height="700",
    scrolling="no", 
    seamless="seamless", 
    frameBorder="0"
  )

```
</div>

---
